The Three-HITs Theorem\footnote{This work was partially supported by COST Action CA15123.}

### 2017-03-01 Paper/Paper.tex
Continued work on elimination and introduction rule.

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{The Three-HIT Theorem\footnote{This work was partially supported by COST Action CA15123.}}
\titlerunning{The Three-HIT Theorem} %optional, in case that the title is too long; the running title should fit into the top page column

@@

@@

\newcommand{\hpushout}[0]{\operatorname{\textbf{hpushout}}}
\newcommand{\hocolim}[0]{\operatorname{\textbf{hocolim}}}
\newcommand{\seg}[0]{\operatorname{\textbf{seg}}}
\newcommand{\inl}[0]{\operatorname{\textbf{inl}}}
\newcommand{\inr}[0]{\operatorname{\textbf{inr}}}
\newcommand{\glue}[0]{\operatorname{\textbf{glue}}}
\newcommand{\inc}[0]{\operatorname{\textbf{inc}}}
\newcommand{\com}[0]{\operatorname{\textbf{com}}}
\newcommand{\Type}[0]{\operatorname{\textsc{Type}}}
\newcommand{\pt}[0]{*}

@@

The goal of this paper is to show that the higher inductive types defined in \cite{basoldhigher} can be generated from the interval, homotopy pushouts and colimits, and that formally justifies this intuition on higher inductive types, 
Also, this generalizes the results in \cite{doorn2016constructing,kraus2014general,kraus2016constructions} where the result is showed for truncations.
With this result the metatheory of higher inductive types could be simplified significantly, because rather than a general class, one only needs to check metatheoretical properties for three types.

@@

Before giving the definition, let us think about how it should be given.
By Ad\'amek's theorem, every inductive type can be given as a colimit.
An inductive type $T$ is given by a polynomial functor $F$ and a constructor $c : F \> T \rightarrow T$, and then $T$ is the colimit of the sequence
\[
\xymatrix
{
	\zero \ar[r] & F \> \zero  \ar[r] & F(F \> \zero) \ar[r] & \ldots
}
\]
To understand what this does, let us assume that $F \> X = X + 1$, so that $T = \mathbb{N}$.
This means we have two inclusions  $\xymatrix{1 \ar[r] & 1+X}$ and  $\xymatrix{X \ar[r] & 1+X}$, and we call them $0_C$ and $S_C$ respectively.
At every step we formally add for each $x : X$ a successor $S_C \> x$, and we add $0_C$.
Repeatedly applying this construction to the empty type $\zero$ gives the natural numbers $\mathbb{N}$.

@@

\begin{definition}
Let a higher inductive type $H$ be given as before, and let the type $H_{\Con}$ be defined as before.
Then we define the \emph{approximator} $H_{\Approx}$, which has a parameter $P$, of $H$ the following pushout
\[
\xymatrix
{
	\sum_{i = 1}^m ((\one + \one) \times B_i \> P) \ar[d]_{t_i + r_i} \ar[r]^-\delta & \sum_{i = 1}^m (I^1 \times B_i \> P) \ar[d]\\
	H_{\Con} \> P \ar[r]_{q_1} & H_{\Approx} \> P
}
\]
Note that this can be written as the homotopy pushout.
\end{definition}

\begin{definition}
In the setting as described, we can define a sequence of approximations to $H$ as follows
\begin{align*}
F \> 0 &= H_{\nonrec},\\
F(n+1) &= H_{\Approx}(F \> n) \qedhere
\end{align*}
\end{definition}

For the colimit we also need maps $f \> n : F \> n \rightarrow F(n + 1)$.
Note that we always have the following sequence of maps
\[
\xymatrix@1
{
	P \ar[r] & H_{\Con} \> P \ar[r] & H_{\Approx} P.
}
\]
Taking $P$ to be $F \> n$, then we have $F (n+1) = H_{\Approx} (F \> n)$, and thus the composition gives the map $F \> n \rightarrow F(n + 1)$.

\section{The Rules}
\label{sec:rules}
Now we have a candidate for the higher inductive type, namely $\hocolim \> F \> f$.
In this section we shall prove that we can define the introduction rules, the eliminator, and show the computation rules.
We will do this step by step, and refer to lemmata in Section \ref{sec:Lemmata}.

@@

Let us start by defining a map $A_{\nonrec} \rightarrow \hocolim \> F \> f$ which gives the introduction rule for the nonrecursive point constructors.
Since $F \> 0$ is defined by $H_{\nonrec}$, which has a constructor $c'_{\nonrec} : A_{\nonrec} \rightarrow H_{\nonrec}$, this can be defined by the following composition.
\[
\xymatrix
{
	A_{\nonrec} \ar[rr]^-{c'_{\nonrec}}
		& & F \> 0 \ar[rr]^-{\inc}
		& & \hocolim \> F \> f
}
\]

Next we show that we also have the recursive constructor meaning that we have a map $A_{\rec} \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
This is slightly more complicated, and for that we first need a lemma which says that colimits over $\mathbb{N}$ commute with polynomials.

@@

Now we will construct the map $A_{\rec} \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$, and by Lemma \ref{lem:colim_commute_poly} it suffices to make a map $\hocolim \> (A_{\rec} \circ F) \> (A \> f) \rightarrow \hocolim \> F \> f$.
For this we use the recursion rule of $\hocolim$, and we start with the following string of maps
\[
\xymatrix
{
		A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} 
		& H_{\rec}(F \> n) \ar[rr]^{\term \circ \iota_1} &
		& H_{\Con}(F \> n) \ar[r]^-{q_1}
		& H_{\Approx}(F \> n) = F(n + 1)
}
\]
where the map $H_{\rec}(F \> n) \rightarrow H_{\Con}(F \> n)$ is the inclusion and the map $H_{\Con}(F \> n) \rightarrow H_{\Approx}(F \> n)$ is the pushout map.
Composing this map with $\inc$, gives maps $A_{\rec}(F \> n) \rightarrow \hocolim \> F \> f$ for all $n : \mathbb{N}$.

Next we need to show the commutativity of the following triangle.
\[
\xymatrix
{
	A_{\rec}(F \> n) \ar[rr]^{A \> f \> n} \ar[dr] & & A_{\rec}(F(n+1)) \ar[dl] \\
	& \hocolim \> F \> f &
}
\]
Let us start with the following rectangle
\[
\xymatrix
{
	A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} \ar[d]_{A \> f \> n} 
		& H_{\rec}(F \> n) \ar[rr]^{\term \circ \iota_1} \ar[d]_{H_{\rec} \> f \> n} &
		& H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> f \> n}\\
	A_{\rec}(F(n+1)) \ar[r]_-{c_{\rec}'} 
		& H_{\rec}(F(n+1)) \ar[rr]_{\term \circ \iota_1} &
		& H_{\Con}(F(n+1))
}
\]
The left square commutes, because by definition of $H_{\rec} \> f$ we have
\[
H_{\rec} \> f \> n \> (c_{\rec}' x) = c_{\rec}' (A_{\rec} \> f \> n \> x).
\]
For a similar reason the right triangle commutes as well.
Hence, it suffices to show that the following diagram commutes.
\[
\xymatrix
{
	H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> f \> n} \ar[r]^-{q_1}
		& H_{\Approx}(F \> n) \ar[d]^{f \> n}\\
	H_{\Con}(F(n+1)) \ar[r]_-{q_1}
		& H_{\Approx}(F(n+1))
}
\]
By expanding the definitions, we see that $H_{\Approx}(F \> n) \rightarrow H_{\Approx}(F(n+1))$ is defined by $p_1 \circ \term \circ \iota_1$.
This means that it suffices to show that the upper triangle in the following square commutes.
\[
\xymatrix
{
	H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> f \> n} \ar[r]^{p_1}
	& H_{\Approx}(F \> n) \ar[d]^{f \> n} \ar[dl]|{\term \circ \iota_0}\\
	H_{\Con}(F(n+1)) \ar[r]_{p_1}
	& H_{\Approx}(F(n+1))
}
\]
The upper triangle commutes by definition.
All in all, we get the desired map
\[
\xymatrix
{
	A \> (\hocolim \> F \> f) \ar[r] & \hocolim \> (A \circ F) \> (A \> f) \ar[r] & \hocolim \> F \> f
}
\]

Next we need to define the introduction rules for the paths.
For this we first need to observe that a type $X$ has the paths $p_i : \prod (x : B_i \> X), t_i = r_i$ iff the following diagram is a pushout
\[
\xymatrix
{
	\sum_{i = 1}^m \two \times (B_i \> X) \ar[r] \ar[d]_{t_i + r_i} & \sum_{i = 1}^m B_i \> X \times I^1 \ar[d]\\
	X \ar[r] & X
}
\]
We shall use this observation to show that $\hocolim \> F \> f$ has the right paths.
Taking $X$ to be $\hocolim \> F \> f$, we thus need to show the following diagram is a pushout.
\[
\xymatrix
{
	\sum_{i = 1}^m \two \times (B_i \> (\hocolim \> F \> f)) \ar[r] \ar[d] & \sum_{i = 1}^m I^1 \times (B_i \> (\hocolim \> F \> f)) \ar[d]\\
	\hocolim \> F \> f \ar[r] & \hocolim \> F \> f
}
\]
Note that homotopy colimits commute with products, so we can rewrite it to where the summations are implicit.
\[
\xymatrix
{
	\hocolim \> ((2 \times B_i) \circ F) \> ((2 \times B_i) \> f) \ar[r] \ar[d] & \hocolim \> ((B_i \times I) \circ F) \> ((B_i \times I) \> f) \ar[d]\\
	\hocolim \> F \> f \ar[r] & \hocolim \> F \> f
}
\]
Since homotopy colimits commute with pushouts, it suffices to show that
\[
\xymatrix
{
	\sum_{i=1}^m 2 \times (B_i \> (F \> n)) \ar[r] \ar[d] & \sum_{i=1}^k I^1 \times B_i (F \> n) \ar[d]\\
	F(n+1) \ar[r] & F(n+1)
}
\]
This holds by definition of $F(n+1)$.

\subsection{Elimination Rule}
The next step will be to show that $\hocolim \> F \> f$ has the right eliminator.

\subsection{Computation Rules}

@@

@@

\begin{lemma}
Colimits commute with pullbacks.
\end{lemma}

>>>>

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{The Three-HITs Theorem\footnote{This work was partially supported by COST Action CA15123.}}
\titlerunning{The Three-HITs Theorem} %optional, in case that the title is too long; the running title should fit into the top page column

@@

\newcommand{\conc}[0]{\bullet}

@@

\newcommand{\refl}[0]{\operatorname{\textbf{refl}}}
\newcommand{\hpushout}[0]{\operatorname{\textbf{hpushout}}}
\newcommand{\hocolim}[0]{\operatorname{\textbf{hocolim}}}
\newcommand{\seg}[0]{\operatorname{\textbf{seg}}}
\newcommand{\inl}[0]{\operatorname{\textbf{inl}}}
\newcommand{\inr}[0]{\operatorname{\textbf{inr}}}
\newcommand{\glue}[0]{\operatorname{\textbf{glue}}}
\newcommand{\inc}[0]{\operatorname{\textbf{inc}}}
\newcommand{\com}[0]{\operatorname{\textbf{com}}}
\newcommand{\Type}[0]{\operatorname{\textsc{Type}}}
\newcommand{\pt}[0]{*}

@@

The goal of this paper is to show that the higher inductive types defined in \cite{basoldhigher} can be generated from the interval, homotopy pushouts and colimits, and that formally justifies this intuition on higher inductive types.
More concretely, we will prove the following theorem.
\begin{theorem}[Three-HITs Theorem]
\label{thm:three-hit}
In Martin-L\"of Type Theory extended with an interval object, homotopy pushouts and colimits, we can define for each higher inductive type as in \cite{basoldhigher} a tye with the same introduction, elimination and computation rules.
\end{theorem}
Also, this generalizes the results in \cite{doorn2016constructing,kraus2014general,kraus2016constructions} where the result is showed for truncations.
With this result the metatheory of higher inductive types could be simplified significantly, because rather than a general class, one only needs to check metatheoretical properties for three types.

@@

Before giving the definition, let us think about how it should be given.
By Ad\'amek's theorem, every inductive type can be given as a colimit.
An inductive type $T$ is given by a polynomial functor $F$ and a constructor $c : F \> T \rightarrow T$, and then $T$ is the colimit of the sequence
\[
\xymatrix
{
	\zero \ar[r] & F \> \zero  \ar[r] & F(F \> \zero) \ar[r] & \ldots
}
\]
To understand what this does, let us assume that $F \> X = 1 + X$, so that $T = \mathbb{N}$.
This means we have two inclusions  $\xymatrix{1 \ar[r] & 1+X}$ and  $\xymatrix{X \ar[r] & 1+X}$, and we call them $0_C$ and $S_C$ respectively.
At every step we formally add for each $x : X$ a successor $S_C \> x$, and we add $0_C$.
Repeatedly applying this construction to the empty type $\zero$ gives the natural numbers $\mathbb{N}$.

@@

Now we have enough to define the approximator.
During the construction one also needs to pay attention to coherency.
For example, in $P$ we have $c_{\nonrec}$, so in $H_{\Approx} \> P$ we might have duplicates of some terms.
By tweaking the pushout a little bit, one can easily solve these coherency problems.

\begin{definition}
Let a higher inductive type $H$ be given as before, and let the type $H_{\Con}$ be defined as before.
Then we define the \emph{approximator} $H_{\Approx}$, which has a parameters $P, Q$ and $f : Q \rightarrow P$, of $H$ the following pushout
\[
\xymatrix
{
	((\one + \one) \times B_i \> P) + H_{\Con} \> Q \ar[d]_{\overline{t_i} + \overline{r_i} + H_{\Con} \> f} \ar[rr]^-{\delta + \inl} & & (I^1 \times B_i \> P) + H_{\Approx} Q  \ar[d]^{\inr}\\
	H_{\Con} \> P \ar[rr]_{\inl} & & H_{\Approx} \> P
}
\]
Note that this can be written as the homotopy pushout.
\end{definition}

\begin{definition}
In the setting as described, we simultaneously define a sequence of approximations $F : \mathbb{N} \rightarrow \Type$ to $H$ and maps $f : \prod(n : \mathbb{N}), F \> n \rightarrow F(n+1)$ as follows
\begin{align*}
F \> 0 &= H_{\nonrec},\\
F \> 1 &= H_{\Approx} \> (F \> 0) \> \zero \> (\zero\frec (F \> 0))\\
F(n+2) &= H_{\Approx} \> (F(n+1)) \> (F \> n) \> (f \> n) \qedhere
\end{align*}
For the maps maps $f \> n : F \> n \rightarrow F(n + 1)$, note that we always have the following sequence of maps
\[
\xymatrix@1
{
	P \ar[r] & H_{\Con} \> P \ar[r] & H_{\Approx} P.
}
\]
Taking $P$ to be $F \> n$, then we have $F (n+1) = H_{\Approx} (F \> n)$, and thus the composition gives the map $F \> n \rightarrow F(n + 1)$.
\end{definition}

\section{The Rules}
\label{sec:rules}
Now we have defined an object $\hocolim \> F \> f$, which is supposed to interpret the higher inductive type.
In order to finish the proof of Theorem \ref{thm:three-hit}, we need to show that it satisfies the rules.
This means that we have to make functions which interpret the introduction rules, and an eliminator such that the computation rules are satisfied.
We will do this step by step, and refer to lemmata in Section \ref{sec:Lemmata} when needed.

@@

Let us start by defining a map $A_{\nonrec} \rightarrow \hocolim \> F \> f$ which gives the introduction rule for the nonrecursive point constructor.
Since $F \> 0$ is defined by $H_{\nonrec}$, which has a constructor $c'_{\nonrec} : A_{\nonrec} \rightarrow H_{\nonrec}$, this can be defined by the following composition.
\[
\xymatrix
{
	A_{\nonrec} \ar[rr]^-{c'_{\nonrec}}
		& & F \> 0 \ar[rr]^-{\inc \> 0}
		& & \hocolim \> F \> f
}
\]

Next we show that we also have the recursive point constructor meaning that we have a map $A_{\rec} \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
This is slightly more complicated, and for that we first need a lemma which says that colimits over $\mathbb{N}$ commute with polynomials.

@@

Now we will construct the map $A_{\rec} \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$, and by Lemma \ref{lem:colim_commute_poly} it suffices to make a map $\hocolim \> (A_{\rec} \circ F) \> (A \> f) \rightarrow \hocolim \> F \> f$.
For this we use the recursion rule of $\hocolim$, and we start with the following string of maps
\[
\xymatrix
{
		A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} 
		& H_{\rec}(F \> n) \ar[rr]^{\term \circ \iota_2} &
		& H_{\Con}(F \> n) \ar[r]^-{\inl}
		& H_{\Approx}(F \> n) = F(n + 1)
}
\]
where the map $H_{\rec}(F \> n) \rightarrow H_{\Con}(F \> n)$ is the inclusion and the map $H_{\Con}(F \> n) \rightarrow H_{\Approx}(F \> n)$ is the pushout map.
Composing this map with $\inc$, gives maps $A_{\rec}(F \> n) \rightarrow \hocolim \> F \> f$ for all $n : \mathbb{N}$.

Next we need to show the commutativity of the following triangle.
\[
\xymatrix
{
	A_{\rec}(F \> n) \ar[rr]^{A_{\rec}(f \> n)} \ar[dr] & & A_{\rec}(F(n+1)) \ar[dl] \\
	& \hocolim \> F \> f &
}
\]
Before we continue, let us recall that inductive types are functors.
Suppose, we have an inductive type $T$ with a parameter $P$, then a function $f : P \rightarrow Q$ gives a function $T \> f : T \> P \rightarrow T \> Q$.
Let us start with the following rectangle
\[
\xymatrix
{
	A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} \ar[d]_{A_{\rec}(f \> n)} 
		& H_{\rec}(F \> n) \ar[rr]^{\term \circ \iota_2} \ar[d]_{H_{\rec}(f \> n)} &
		& H_{\Con}(F \> n) \ar[d]_{H_{\Con}(f \> n)}\\
	A_{\rec}(F(n+1)) \ar[r]_-{c_{\rec}'} 
		& H_{\rec}(F(n+1)) \ar[rr]_{\term \circ \iota_2} &
		& H_{\Con}(F(n+1))
}
\]
The left square commutes, because by definition of $H_{\rec} \> f$ we have
\[
H_{\rec} \>(f \> n) \> (c_{\rec}' x) = c_{\rec}' (A_{\rec} \> (f \> n) \> x).
\]
For a similar reason the right triangle commutes as well.
Hence, it suffices to show that the following diagram commutes.
\[
\xymatrix
{
	H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> (f \> n)} \ar[r]^-{\inl}
		& H_{\Approx}(F \> n) \ar[d]^{f(n+1)}\\
	H_{\Con}(F(n+1)) \ar[r]_-{\inl}
		& H_{\Approx}(F(n+1))
}
\]
Note that $H_{\Approx}(F(n+1)) = F(n+2)$ and $H_{\Approx}(F \> n) = F(n+1)$.
Hence, this diagram commutes, because of the pushout.

Next we need to define the introduction rules for the paths.
Let us start by making a map $\sum_{i = 1}^m I^1 \times B_i \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
Since homotopy colimits commute with polynomials, it suffices to make a map $\hocolim \> (I^1 \times B_i \> F) \> (I^1 \> B_i \> f)  \rightarrow \hocolim \> F \> f$.

For this we use the eliminator of the homotopy colimit.
First, we need to make for all $n$ a map $I^1 \times B_i \> (F \> n)  \rightarrow \hocolim \> F \> f$.
By definition we have the following string of maps
\[
\xymatrix
{
	I^1 \times B_i \> (F \> n) \ar[rr]^-{\inr} & & F(n+1) \ar[rr]^-{\inc(n+1)} & & \hocolim \> F \> f.
}
\]
Next we need to show that the following diagram commutes.
\[
\xymatrix
{
	I^1 \times B_i \> (F \> n) \ar[rr]^-{\inr} \ar[d]_{I^1 \times B_i \> (f \> n)} & & F(n+1) \ar[d]^{f(n+1)}\\
	I^1 \times B_i \> (F(n+1)) \ar[rr]^-{\inr} & & F(n+2)
}
\]
This can be proven by induction on $B_i$, and using the definition of $I^1 \times B_i \> (f \> n)$.
We can use the path $\refl$.
All in all, we get a map $p_i : \hocolim \> (I^1 \times B_i \> F) \> (I^1 \times B_i \> f) \rightarrow \hocolim \> F \> f$

Now we have the following diagram
\[
\xymatrix
{
	2 \times B_i(\hocolim \> F \> f) \ar[r] \ar[dr]_{\overline{t_i} + \overline{r_i}} & I^1 \times B_i(\hocolim \> F \> f) \ar[r] & \hocolim \> (I^1 \times B_i \> F) \> (I^1 \times B_i \> f) \ar[dl]\\
	& \hocolim \> F \> f
}
\]

$2 \times B_i(\hocolim \> F \> f)$ is isomorphic to $\hocolim \> (2 \times B_i \> F) \> 2 (\times B_i \> f)$.

Induction to second, so we have $(0, x)$ (similar for $1$) and $x : F \> n$.
This gets mapped to $(0, x)$ which is equal to $t_i$ via the path $\glue (\inl (0, x))$.

Remaining:
\begin{equation*}
\begin{split}
\com_*(\ap \> (\inc \> n) \> \glue (\inl (0, x))) = \ap \> (\inc (n+1))) \>\glue (\inl (0, f \> n \> x))\\
(\ap \> \overline{t_i} \> \com)^{-1} \conc \ap \> (\inc \> n) \> \glue (\inl (0, x)) \conc \ap \> p_i \> \com
\end{split}
\end{equation*}
$(\ap \> \overline{t_i} \> \com)^{-1}$ is like $\ap \> (\inc \> n) \> (\ap \> c \> \ldots (\ldots \ap \> \text{coherence path}))$, because of the computation rule of $c_i$.

This is the coherence path which should be added on level $n$.

\subsection{Elimination Rule}
For the next step we define the right eliminator for $\hocolim \> F \> f$. 
For this we suppose that we have
\[
Y : \hocolim \> F \> f \rightarrow \Type
\]
\[
c_{Y, \nonrec} : \prod (a : A_{\nonrec}), Y(c_{\nonrec})
\]
\[
c_{Y, \rec} : \prod (x : A_{\rec} \> \hocolim \> F \> f), \overline{A_{\rec}} \> Y \> x \rightarrow Y(c_{\rec} \> x)
\]
\[
q_{Y, i} : \prod (x : B_i \> H)(h_x : \overline{B_i} \> Y \> x), \hatt_i =_{p_j \, x} \hatr_j
\]
In order to make a map $\prod (x : \hocolim \> F \> f), Y \> x$, we use the induction principle of $\hocolim \> F \> f$, and for that we need to make maps $\prod (x : F \> n), Y(\inc \> n \> x)$.

First we need to make a map $\prod (x : F \> 0), Y(\inc \> 0 \> x)$.
Recall that $F \> 0$ was defined to be $H_{\nonrec}$ which only has a constructor $c'_{\nonrec} : A_{\nonrec} \rightarrow H_{\nonrec}$.
So, let us assume that we have $a : A_{\nonrec}$.
Since $c_{\nonrec} \> a = \inc \> 0 \> (c\_{\nonrec} a)$, it suffices to find an inhabitant of $Y(c_{\nonrec} \> a)$, and for that we take $c_{Y, \nonrec} \> a$.
Hence, we get a map $\prod (x : F \> 0), Y(\inc \> 0 \> x)$.

Now suppose that we have a map $\prod (x : F \> n), Y(\inc \> n \> x)$, and our goal is to make a map $\prod  (x : F(n+1)), Y(\inc \> (n+1) x)$.
In order to do so, we will first look at how to extend it to a map $\prod (x : H_{\Con} (F \> n)), Y(\inc \> (n+1) \> (\inl \> x))$.

Let us do this in the general case.
Suppose that we have $g : P \rightarrow \hocolim \> F \> f$, and that we have $h : \prod (x : P), Y(g \> x)$.
Our goal is to extended the map into a $h' : \prod (x : H_{\rec} P), Y(c_{Y, \rec} \> x)$, and for that we use $H_{\rec}$ induction.
Note that for each $c'_{\rec} \> x$ with $x : A_{\rec} \> P$ we have the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$, and thus we have a type family on $H_{\rec}$.
Now let $x : A_{\rec} \> P$ and $y : \overline{A_{\rec}} \> Y \> x$ be given.
Then we need to give an element of the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$ for which we take
\[
c_{Y,\rec} \> (A_{\rec} \> g \> x) \> y
\]
Now we can also extend the map to $H_{\Con}^n \> P$, because we can define this map on each component.
On the component $P$ it is just $h$, and on the other components we define it via extension.

Next we need to extend the map to $H_{\Approx} \> P \> Q$.
For that we need to make a map $h' : \prod (x : I^1 \times B_i \> P), Y()$

Let $(t, x) : I^1 \times B_i \> P$, and now we use $I^1$ induction.
If $t = 0$, we map it to $\hatt_i (x)$, and for $t = 1$ we map it to $\hatr_i (x)$.
Now the path $q_{Y, i}$ gives the image of $\seg$, and that finishes the induction.

For the commutativity of the diagram note that by definition the dependent map from $H_{\Con} \> P$ to $Y$ sends the constructor term $t_i$ to the lift $\hatt_i$.
This is because the map replaces each $c_{\rec}$ by $c_{Y, \rec}$ which is precisely how the lift was constructed.

Next we do it for the coherency.

Induction on the level (so, ultimately some kind of simultaneous induction?)

Then induction on the depth.

Base case: just induction assumption.

Step case: then it can be worked out from the diagram.

To finish the proof, we need to give the image for the path $\com$.
More concretely, we need to show that $\inc \> n \> x$ and $\inc \> (n+1) \> (f \> x)$ are mapped to the same element.
The map $f : F \> n \rightarrow F(n + 1)$ is defined by the pushout as follows
\[
\xymatrix
{
	((\one + \one) \times B_i \> (F(n+1))) + H_{\Con} \>  (F \> n) \ar[d]_{\overline{t_i} + \overline{r_i} + H_{\Con} \> f} \ar[rr]^-{\delta + \inl} & & (I^1 \times B_i \> (F(n+1))) + F(n+1)  \ar[d]^{\inr}\\
	H_{\Con} \> (F(n+1)) \ar[rr]_{\inl} & & F(n+2)
}
\]
Since the map to $Y$ was defined as the pushout map, it will commute automatically.

All in all, we have acquired a map $\prod (x : \hocolim \> F \> f), Y \> x$, and this way we defined the right eliminator for $\hocolim \> F \> f$.
We shall call the eliminator $H\frec$.

\subsection{Computation Rules}
Lastly, we show that this eliminator also satisfies the computation rules.
First, we prove that for each $t : A_{\rec}(\hocolim \> F \> f)$ that $H\frec(c_{\rec} \> t) \equiv f_i \> t \> (\overline{A_{\rec}} H\frec t)$.
Again we use that colimits commute with polynomials.

Let $n : \mathbb{N}$ and $x : A_{\rec}(F \> n)$.
Then by the computation rules we have
\begin{equation*}
\begin{split}
H\frec(c_{\rec} \> x) 
&\equiv H\frec(\inc \> (n+1) \> (c_{\rec}' x)) \\
&\equiv c_{Y,\rec} \> (A_{\rec} \> (\inc \> n) \> x) \> (\overline{A} \> H\frec \> x)\\
\end{split}
\end{equation*}
Hence, we can always take $\refl$ to be the path.
This will also give an image for $\com$, and thus the computation rules for the points are satisfied.

Note that the this computation rule is a propositional equality.
This is logical, because it is proven all $x : A_{\rec}(F \> n)$.
However, for closed terms, we have a definitional equality.
This is because $c_{\nonrec} \> a$ for $a : A_{\nonrec}$ is defined to be$\inc \> 0 \> (c_{\nonrec}' \> a)$.
All the closed terms are thus inhabitants of some $F \> n$, and since at every step the equalities are definitional, we can conclude that for closed terms the equality is definitional.

Now we show the computation rules for the paths.

@@

\begin{lemma}
$\hocolim \> (\lambda n . A) \> \operatorname{Id}$ is $A$.
\end{lemma}

@@
